Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-25 doc/main_jfm.tex
edited up to end of 3.1

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integral Equation Method}
\label{sec:IEM}
Computing the hydrophobic attraction potential and the particle forces
and torques requires the solution of elliptic partial differential
equations (PDEs) in an unbounded complex domain. We recast both these
PDEs as boundary integral equations (BIEs). We discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
Integrals that are smooth are computed with the spectrally-accurate
quadrature rule, and nearly-singular integrals, caused by close contact
between two particles, are computed with a high-order
interpolation-based quadrature rule~\cite{qua-bir2014}. After
discretizing and applying quadrature, the resulting linear system is
solved with matrix-free GMRES, and we guarantee that the number of GMRES
iterations is mesh-independent by using second-kind BIEs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to our previous work~\cite{Fu20}, we represent the HAP as a
double-layer potential
\begin{align}
  \label{eq:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \mathbb{R}^2,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind and the integral is taken in the sense of principle value whenever $\xx \in \partial \Omega$. 
By requiring that the density function $\sigma$ satisfies the
second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. We
solve~\eqref{eq:screenedSKIE} with a collocation method. The integrals
are approximated with either the trapezoid rule or with the
interpolation-based near-singular integration scheme. This results in a
$NN_b \times NN_b$ linear system that is solved with a block-diagonal
preconditioned GMRES solver.

To calculate the hydrophobic force and torque, the gradient of the
double-layer potential~\eqref{eq:HAP_DLP} must be computed on the
boundary of each particle. In Section~\ref{subsec:calculating_force}, we
show that the force and torque calculations can be expressed in terms of
non-singular integrals.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Integral Equation Method}
\label{sec:IEM}
Computing the hydrophobic attraction potential and the particle forces
and torques requires the solution of elliptic partial differential
equations (PDEs) in an unbounded complex domain. We recast both these
PDEs as boundary integral equations (BIEs). We discretize each BIE at
$N$ points on each of the $N_b$ particles with a collocation method.
Integrals that are smooth are computed with the spectrally-accurate
trapezoid rule, and nearly-singular integrals, caused by close contact
between two particles, are computed with a high-order
interpolation-based quadrature rule (\cite{qua-bir2014}). After
discretizing and applying quadrature, the resulting linear system is
solved with matrix-free GMRES, and we guarantee that the number of GMRES
iterations is mesh-independent by using second-kind BIEs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{HAP Boundary Integral Equation}
Similar to our previous work (\cite{Fu20}), we represent the HAP as a
double-layer potential
\begin{align}
  \label{eq:HAP_DLP}
  u(\xx) = \frac{1}{2\pi} \int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \Omega,
\end{align}
where $K_0$ is the zeroth-order modified Bessel function of the first
kind and the integral is taken in the sense of principle value whenever $\xx \in \partial \Omega$. 
By requiring that the density function $\sigma$ satisfies the
second-kind integral equation
\begin{equation}
\label{eq:screenedSKIE}
  f(\xx) = \frac{1}{2}\sigma(\xx) + 
    \frac{1}{2\pi}\int_{\bd\Omega} \pderiv{}{\nnu_\yy}
    K_0 \left(\frac{|\xx - \yy|}{\rho}\right) \sigma(\yy) \, \dif s_\yy,
    \quad \xx \in \bd\Omega,
\end{equation}
the HAP double-layer potential~\eqref{eq:HAP_DLP} satisfies the screened
Laplace equation~\eqref{eq:SL}--\eqref{eq:SLff}. After
discretizing~\eqref{eq:screenedSKIE}, the result is a $NN_b \times NN_b$
linear system that is solved with block-diagonal preconditioned GMRES.

To calculate the hydrophobic force and torque, the gradient of the
double-layer potential~\eqref{eq:HAP_DLP} must be computed on the
boundary of each particle. The resulting integrands are singular, and
specialized quadrature would be necessary to approximate such integrals.
Alternatively, in Section~\ref{subsec:calculating_force}, we show that
the force and torque calculations can be expressed in terms of
non-singular integrals.
